\addcontentsline{toc}{section}{References}
\begin{thebibliography}{100}

\bibitem[Santana, 2017]{Santana17} Santana, E. (2017). Keras plays catch, a single file Reinforcement Learning example - Eder Santana. [online] Edersantana.github.io. Available at: \url{https://edersantana.github.io/articles/keras_rl/} [Accessed 12 Dec. 2017].

\bibitem[Harvey, 2017]{Harvey17} Harvey, M. (2017). Using reinforcement learning in Python to teach a virtual car to avoid obstacles. [online] Coastline Automation. Available at: \url{https://blog.coast.ai/using-reinforcement-learning-in-python-to-teach-a-virtual-car-to-avoid-obstacles-6e782cc7d4c6} [Accessed 12 Dec. 2017].
 
\bibitem[Harvey, 2017]{Harvey2017} Harvey, M. (2017). harvitronix/reinforcement-learning-car. [online] GitHub. Available at: \url{https://github.com/harvitronix/reinforcement-learning-car} [Accessed 12 Dec. 2017].

\bibitem[Orlin, 2017]{Orlin} Orlin, B. (2017). Ultimate Tic-Tac-Toe. [online] Math with Bad Drawings. Available at: \url{https://mathwithbaddrawings.com/2013/06/16/ultimate-tic-tac-toe/} [Accessed 12 Dec. 2017].

\bibitem[Roberston, 2017]{Robertson} Robertson, J. (2017). jjrob13/deep\_ultimate\_tic\_tac\_toe. [online] GitHub. Available at: \url{https://github.com/jjrob13/deep_ultimate_tic_tac_toe} [Accessed 12 Dec. 2017].

\bibitem[Keras.io, 2017]{Keras} Keras.io. (2017). Keras Documentation. [online] Available at: \url{https://keras.io/} [Accessed 12 Dec. 2017].

\bibitem[Matiisen, 2017]{Matiisen}  Matiisen, T. (2017). Guest Post (Part I): Demystifying Deep Reinforcement Learning - Intel Nervana. [online] Intel Nervana. Available at: \url{https://www.intelnervana.com/demystifying-deep-reinforcement-learning/} [Accessed 12 Dec. 2017].

\end{thebibliography}